Climatic warming strengthens a positive feedback\\ between alpine shrubs and fire

### 2016-04-11 manuscript/manuscript.Rnw
edit to acknowledgements and to signifiance statement

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Temperatures are rapidly increasing in alpine and tundra ecosystems worldwide. A consequence of this temperature increase has been significant increases in shrub cover and a predicted increase in the frequency or severity of fires. Here we use experiemental and observational data to explore whether there are antagonistic or synergistic feedbacks between temperature, fire and shrub demographic rates. We find that increases in temperatures, coupled with more frequent or severe fire is likely to exacerbate the rate of shrub cover increases, and consquently, increase landscape flammability.}

@@

\acknow{
This research was funded through Australian Research Council Linkage Grants, partnered through the Department of Sustainability and Environment, Parks Victoria, Commonwealth Scientific and Industrial Research Organisation (CSIRO). Funding was also received from the Centre of Excellence for Environmental Decisions (CEED) and Holsworth Research Committee. J.S.C was a recipient of an Australian Postgraduate Award. Monica Camac, Brad Farmilo, Monica Hursburgh, Paulius Kviecinskas, Karen Stott, Imogen Fraser, Sarah Bartlett, Paul Smart, Steven Rumbold, Lachlan Yourn and Chris Jones provided assistance with field measurements. William Morris and John Baumgartner provided coding advice and Warwick Papst provided field logistic advice. Daniel Falster and Richard Fitzjohn for developing software that enabled these analyses to be readily reproducible. Special thanks to David Bowman, Ana{\"i}s Gibert, John Morgan, Kimberley Millers, Michaela Plein and Inka Veltheim for their comments on this manuscript.}

>>>>

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Temperatures are rapidly increasing in alpine and tundra ecosystems worldwide. A consequence of this is an increase in shrub cover and in the frequency/ severity of fires. Here we use experimental and observational data to explore whether there are antagonistic or synergistic feedbacks between temperature, fire and shrub demographic rates. We find that feedback loops are likely to be synergistic; increases in temperature and fire will likely accelerate the rate of shrub cover increase, and this in turn will increase flammability, changing the composition of the vegetation in this landscape.}

@@

\acknow{
This research was funded through Australian Research Council Linkage Grants, partnered through the Department of Sustainability and Environment, Parks Victoria, Commonwealth Scientific and Industrial Research Organisation (CSIRO). Funding was also received from the Centre of Excellence for Environmental Decisions (CEED) and Holsworth Research Committee. J.S.C was a recipient of an Australian Postgraduate Award. Monica Camac, Brad Farmilo, Monica Hursburgh, Paulius Kviecinskas, Karen Stott, Imogen Fraser, Sarah Bartlett, Paul Smart, Steven Rumbold, Lachlan Yourn and Chris Jones provided assistance with field measurements. William Morris and John Baumgartner provided coding advice and Warwick Papst provided field logistic advice. Daniel Falster and Richard Fitzjohn for developing software that enabled these analyses to be readily reproducible. Special thanks to John Baumgartner, David Bowman, Manuel Esper\'{o}n-Rodr\'{i}guez, Ana{\"i}s Gibert, John Morgan, Kimberley Millers, Michaela Plein and Inka Veltheim for their comments on this manuscript.}
